A Theory of Bidirectional Type Synthesis for Simple Types

### 2023-07-10 tex/BiSig.tex
[ tex ] ‘Beyond syntax-directed type systems’ in S7
[ tex ] Done with S5 for now
[ tex ] Turn on `anonymous` and `review`

\documentclass[acmsmall,screen]{acmart}

@@

\AtEndPreamble{%
\theoremstyle{acmdefinition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem*{claim}{Claim}
\newtheorem{claimproof}{Proof of Claim}
}

@@

\begin{acks}
%We thank Nathanael Arkor for the useful conversation.
We thank Kuen-Bang {Hou (Favonia)} for his comments and suggestions.
The work is supported by the Ministry of Science and Technology of Taiwan under grant MOST 109-2222-E-001-002-MY3.
\end{acks}

>>>>

\documentclass[acmsmall,screen,review,anonymous,draft]{acmart}

@@

\AtEndPreamble{%
\newtheorem*{claim}{Claim}
\theoremstyle{acmdefinition}
\newtheorem*{claimproof}{Proof of Claim}
\newtheorem{remark}[theorem]{Remark}
}

@@

\begin{acks}
%We thank Nathanael Arkor for the useful conversation.
We thank Kuen-Bang {Hou (Favonia)} for his comments and suggestions.
The work is supported by the \grantsponsor{NSTC}{National Science and Technology Council of Taiwan}{https://www.nstc.gov.tw/} under grant \grantnum{NSTC}{NSTC 112-2221-E-001-003-MY3}.
\end{acks}
